Supplementary Materials

### 2021-01-21 analysis/analysis.Rmd
minor sup mat edits

Here we import our data and make some summary plots.

@@

The table below shows how many groups per participant we have data for.

```{r}
d_dispthresh %>% 
  group_by(subject) %>% 
  summarise(count = n(), .groups = "drop") %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

@@

In addition to the primary SSVEP data set, we are also importing two control data sets which are (a) even harmonic data from the same occipital electrodes, and (b) odd harmonic data from six parietal electrodes (see Figure 1.1 and the main paper).

@@

Information on the symmetries and subgroups contained within each wallpaper group was obtained from <cite> and is summarised in the files `symmeries_in_group.csv`, `subgroup_relations.csv`, and `subgroup_normal.csv`.

@@

knitr::kable(sym_dat, caption = "wallpaper group summary") %>% 
    kableExtra::kable_styling(full_width = F)
```

@@

*  Use weakly-informative priors.
*  Fit a multi-level model using the lognormal distribution.
  + independent variable (wallpaper group) and one dependent variable (rms or threshold).
  + maximal random effect structure.
* Check model fit ($r^2$ statistics and trace plots).
* Extract mcmc samples from the posterior distributions.
* Use these samples to estimate the difference between sub- and supergroups.

@@

Our independent variable is a categorical factor with 16 levels. We will drop the intercept from our model and instead fit a coefficient for each factor level ($y \sim x - 0$). As our defendant variable will be log-transformed, we can use the priors below:

>>>>

First we import our data and make some summary plots.

@@

@@

In addition to the primary SSVEP data set, we are also importing two control EEG data sets which are (a) even harmonic data from the same occipital electrodes, and (b) odd harmonic data from six parietal electrodes (see Figure 1.1 and the main paper).

@@

Information on the symmetries and subgroups contained within each wallpaper group was obtained from Coxeter & Moses (1980, Generators and Relations
for Discrete Groups) and is summarised in the files `symmeries_in_group.csv`, `subgroup_relations.csv`, and `subgroup_normal.csv`.

@@

knitr::kable(sym_dat, caption = "Wallpaper group summary") %>% 
    kableExtra::kable_styling(full_width = F)
```

@@

*  Use weakly-informative priors.
*  Fit a multi-level model using the lognormal distribution.
  + independent variable (wallpaper group) and one dependent variable (rms or threshold).
  + maximal random effect structure.
* Extract mcmc samples from the posterior distributions.
* Use these samples to estimate the difference between sub- and supergroups.

@@

Our independent variable is a categorical factor with 16 levels. We will drop the intercept from our model and instead fit a coefficient for each factor level ($y \sim x - 0$). As our dependent variable will be log-transformed, we can use the priors below:
